Adaptive Scheduling of Scientific Workflows

### 2024-03-22 main.tex
temp

The idea is to get rid of the constraint that a processor handles a {\em block} of tasks,
but favor processor reuse as is done in HEFT.

@@

@@

In this case ($Res >0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data. For now, we propose a greedy approach,
evicting the largest files of $\PD_j$ until $Res$ data has been evicted. 
\AB{I can further detail if needed, moving data of $\PD_j$ from $\curM_j$
to $\curC_j$, and removing it from $\PD_j$...}
If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
we set the finish time to~$+\infty$ (invalid choice).

@@

>>>>

The idea is to get rid of the constraint that a processor handles a {\em block} of tasks,
but favor processor reuse as is done in HEFT. 
Furthermore, this would allow us to handle variability on the fly, by updating
the bottom levels if some parameters vary, and computing the schedule
only for the near future...

@@

 HEFTM-BLC: from the study of the fork (see below), it seems important
 to also account for the size of the data as input of a task,
 to give more priority at tasks with potential large incoming communications.
 For each task, we compute its modified bottom level: 
 $$blc(u) = bl(u) + \max_{(v,u)\in E} c_{v,u}   . $$

@@

In this case ($Res >0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data. For now, we propose a greedy approach,
evicting the smallest files of $\PD_j$ until $Res$ data has been evicted,
in order to avoid costly communications. 
\AB{FYI We initially discussed  evicting the largest files, but this leads to 
large communications and does not seem efficient after all... Maybe we can think of another 
approach that would take into account both data size and bottom level...}
\AB{I can further detail if needed, moving data of $\PD_j$ from $\curM_j$
to $\curC_j$, and removing it from $\PD_j$...}
If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
we set the finish time to~$+\infty$ (invalid choice).

@@

\subsection{The fork}
We look at the behavior of these heuristics on a fork graph,
where there is a root task~$T_0$, producing $n$ files $f_1, \ldots, f_n$
to be used by tasks $T_1, \ldots, T_n$ ($f_i = c_{0,i}$).

Without memory, this problem is NP-complete; this is equivalent
to 2-partition if the tasks have $w_i=a_i$, and all files are of size~$f_i=0$,
and with two processors. Half of the tasks must be sent to the processor
on which $T_0$ is not executed, and the optimal makespan is 
$w_0+\frac{1}{2}\sum_{1\leq i \leq n} w_i$.

However, with an infinite number of identical processors, it can be
solved in polynomial time: sort tasks by non-decreasing $f_i+w_i$; 
the $k$ tasks with smallest $f_i+w_i$ are then sent to another processor,
while the remaining $n-k$ tasks are executed locally (try all values of $k$).

With heterogeneous processors, it is probably NP-complete again
because we could ensure that there are only two processors fast enough
and get back to the 2-partition...

We also had an example where evicting large files first in step 2
can lead to arbitrarily bad makespan. Consider a fork with $n=2$,
$f_1=1$, $w_1=2$, $f_2=100$, $w_2=1$, and memory constraint
imposes that we free one unit of memory before executing one
of the tasks... Actually the new version with BLC would start 
considering $T_2$ and be fine in this case...

\AB{Can we prove that we have (maybe) a 2-approximation, 
at least for the fork? What worst-case can we think of? }
